Convex Surrogates via Polyhedral Losses

### 2019-02-02 cvx-fin.tex
some comments suggested by Raf

\subsection{Example}
We give an example of how this necessary condition can be applied to prove a lower bound.
The \emph{abstain property} sets a threshold of $\alpha$ (here, $\alpha=0.5$) and has $\R = \Y \cup \{\text{abstain}\}$.
We have $\text{abstain} \in \gamma(p) \iff \max_y p_y \leq \alpha$, and $y \in \gamma(p) \iff p_y = \max_{y'} p_{y'}, p_y \geq \alpha$.
In other words, it is similar to the mode, except that if none of the options has a high enough probability, the best report is to abstain.
\citet{ramaswamy2018consistent} show that this property on $|\Y|=n$ can be embedded in $\lceil \log_2(n) \rceil$ dimensions.
Their construction is quite beautiful and extremely instructive for studying embeddings.
Prior to this work, it was not known if one could improve by embedding abstain($0.5$) on $5$ or more outcomes in $\reals^2$.

@@

\begin{conjecture}\label{conj:abstain-tight}
  Abstain with $\alpha=1/2$ is $(\log_2 |\Y|)$-embeddable, but no lower.
\end{conjecture}

>>>>

\subsection{Example}
We give an example of how this necessary condition can be applied to prove a lower bound.
The \emph{abstain property} sets a threshold of $\alpha$ (here, $\alpha=0.5$) and has $\R = \Y \cup \{\text{abstain}\}$.
We have $\text{abstain} \in \gamma(p) \iff \max_y p_y \leq \alpha$, and $y \in \gamma(p) \iff p_y = \max_{y'} p_{y'}, p_y \geq \alpha$.
In other words, it is similar to the mode, except that if none of the options has a high enough probability, the best report is to abstain.
\citet{ramaswamy2018consistent} show that this property on $|\Y|=n$ can be embedded in $\lceil \log_2(n) \rceil$ dimensions.
Their construction is quite beautiful and extremely instructive for studying embeddings.
In particular, it shows how to embed abstain$(0.5)$ on $4$ outcomes into $\reals^2$.
Prior to this work, it was not known if one could improve by embedding abstain($0.5$) for $5$ or more outcomes in $\reals^2$.

@@

\paragraph{Implications.}
We conjecture that the construction of \citet{ramaswamy2018consistent} is optimal in all dimensions.
If so, this leaves two possibilities: It might be that there is some \emph{non-embedding} approach that elicits this property using a report space of fewer than $d=\lceil \log_2 |\Y|\rceil$ dimensions.
Going beyond the embedding approach seems to require new ideas that could be relevant to many applications in machine learning.
On the other hand, it might be that the best possible dimension is achieved by an embedding approach and polyhedral loss.
If true, it would be interesting to see how generally this might hold.
\begin{conjecture}\label{conj:abstain-tight}
  Abstain with $\alpha=1/2$ is $(\log_2 |\Y|)$-embeddable, but no lower.
\end{conjecture}
